Hierarchical Reverberation Mapping

### 2013-09-28 Paper/ms.tex
Fixed error
Working ont he abstract

\section{Introduction}
Reverberation mapping (RM) is an important technique that has contributed a
large amount to our knowledge of active galactic nuclei (AGN).

Since its inception, there have been many improvements in the analysis of
reverberation mapping data. These range from methods that attempt to infer the
transfer function \citep{1995ApJ...440..166K, 2011ApJ...735...80Z},
the velocity-resolved transfer function
\citep{2010ApJ...720L..46B}, or the physical structure of the BLR itself
\citep{pancoast, arp151}.

There are deeper issues at play in reverberation mapping, that we will ignore
for the purposes of this letter. We list them here for completeness. Firstly,
the mean lag $\tau$ is not equal to $c$ times the mean radius of the BLR
distribution. Secondly, the mean lag $\tau$ is also not what the common
cross-correlation techniques measures, except in the case of very narrow
transfer functions. Some of these difficulties have been addressed in other
contributions by \citet{pancoast} and \citet{arp151}.

@@

In a hierarchical model, the prior for the parameters $\{\theta_i\}$ is created
by introducing hyperparameters $\alpha$ such that the joint prior for $\alpha$
and the $\{\theta_i\}$ is:
\begin{eqnarray}
p(\alpha, \theta_i) &=& p(\alpha)\prod_{i=1}^N p(\theta_i | \alpha)
\end{eqnarray}
The posterior distribution for
$\btheta = \{\theta_1, ..., \theta_N\}$ and the hyperparameters $\alpha$
given the data 
$\bx = \{x_1, ..., x_N\}$
should actually be
\begin{eqnarray}
p(\alpha, \btheta | \bx) &\propto&
p(\alpha)p(\btheta|\alpha)p(\bx | \btheta, \alpha)\\
&=& p(\alpha)\prod_{i=1}^N f(\theta_i|\alpha)p(x_i | \theta_i)
\end{eqnarray}
The marginal posterior distribution for the hyperparameters $\alpha$ is
\begin{eqnarray}
p(\alpha | \bx) &=&
\int p(\alpha, \btheta|\bx) \, d\btheta\\
&\propto& p(\alpha)\int \prod_{i=1}^N f(\theta_i|\alpha)p(x_i | \theta_i) d^N\theta\\
&\propto& p(\alpha) \prod_{i=1}^N \int f(\theta_i|\alpha)p(x_i | \theta_i) d\theta_i\\
&\propto& p(\alpha) \prod_{i=1}^N \int \frac{f(\theta_i|\alpha)}{\pi(\theta)}p(x_i | \theta_i) \pi(\theta_i)d\theta_i\\
&\propto& p(\alpha) \prod_{i=1}^N \mathds{E}\left[\frac{f(\theta_i|\alpha)}{\pi(\theta)}p(x_i | \theta_i)\right]
\end{eqnarray}
where the expectation is taken with respect to the individual object posterior
of Equation~\ref{eq:individual}. This result enables us to reconstruct the
posterior distribution for the hyperparameters even though the individual object
inferences were made without the hierarchical structure in the prior.

@@

\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Bentz et al.}{2010}]{2010ApJ...720L..46B} 
Bentz M.~C., et al., 2010, ApJ, 720, L46

>>>>

\section{Introduction}
Reverberation mapping (RM) is an important technique for the study
of active galactic nuclei (AGN). The technique is based on the temporal
fluctuations of the central continuum source, and the subsequent response
of the broad line region (BLR) emission. The time delay between the continuum
and the broad line fluctuations provides an estimate of the size of the BLR.

RM is a observationally intensive, requiring observations over a period of
a few tens of days \citep{2013ApJ...769..128B}. As a result, many authors have
studied the data analysis techniques involved in RM, and made substantial
advances. These range from methods that attempt to infer the
transfer function \citep[the distribution of lags in a single object,
e.g.][]{1995ApJ...440..166K, 2011ApJ...735...80Z},
the velocity-resolved transfer function
\citep{2010ApJ...720L..46B}, or the physical structure of the BLR itself
\citep{pancoast, arp151}.

There are many subtleties involved in reverberation mapping, that we will ignore
for the purposes of this letter. We note them here for completeness. Firstly,
the lag $\tau$ is not equal to $c$ times the mean radius of the BLR
distribution. Secondly, the lag $\tau$ is also not what the common
cross-correlation techniques measures, except in the case of very narrow
transfer functions (i.e. only a single lag in the system, rather than a wide
distribution of lags). Some of these difficulties have been addressed in other
contributions by \citet{pancoast} and \citet{arp151}.

@@

In a hierarchical model, the prior for the parameters $\{\theta_i\}$ is created
by introducing hyperparameters $\alpha$ such that the joint prior for $\alpha$
and the $\{\theta_i\}$ is:
\begin{eqnarray}
p(\alpha, \theta_i) &=& p(\alpha)\prod_{i=1}^N p(\theta_i | \alpha)
\end{eqnarray}
The posterior distribution for
$\btheta = \{\theta_1, ..., \theta_N\}$ and the hyperparameters $\alpha$
given the data 
$\bx = \{x_1, ..., x_N\}$
should actually be
\begin{eqnarray}
p(\alpha, \btheta | \bx) &\propto&
p(\alpha)p(\btheta|\alpha)p(\bx | \btheta, \alpha)\\
&=& p(\alpha)\prod_{i=1}^N f(\theta_i|\alpha)p(x_i | \theta_i)
\end{eqnarray}
The marginal posterior distribution for the hyperparameters $\alpha$ is
\begin{eqnarray}
p(\alpha | \bx) &=&
\int p(\alpha, \btheta|\bx) \, d\btheta\\
&\propto& p(\alpha)\int \prod_{i=1}^N f(\theta_i|\alpha)p(x_i | \theta_i) d^N\theta\\
&\propto& p(\alpha) \prod_{i=1}^N \int f(\theta_i|\alpha)p(x_i | \theta_i) d\theta_i\\
&\propto& p(\alpha) \prod_{i=1}^N \int \frac{f(\theta_i|\alpha)}{\pi(\theta)}p(x_i | \theta_i) \pi(\theta_i)d\theta_i\\
&\propto& p(\alpha) \prod_{i=1}^N \mathds{E}\left[\frac{f(\theta_i|\alpha)}{\pi(\theta)}\right]
\end{eqnarray}
where the expectation is taken with respect to the individual object posterior
of Equation~\ref{eq:individual}. This result enables us to reconstruct the
posterior distribution for the hyperparameters even though the individual object
inferences were made without the hierarchical structure in the prior.

@@

\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Barth et al.}{2013}]{2013ApJ...769..128B} 
Barth A.~J., et al., 2013, ApJ, 769, 128

\bibitem[\protect\citeauthoryear{Bentz et al.}{2010}]{2010ApJ...720L..46B} 
Bentz M.~C., et al., 2010, ApJ, 720, L46
